

\documentclass[]{deedy-resume-openfont}
\usepackage{color}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Jason Porter}{\href{mailto:jasonsporter88@gmail.com}{jasonsporter88@gmail.com} | 801.691.4806}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\section{Education}

\runsubsection{Brigham Young University}
\descript{| Mechanical Engineering }
\location{Expected Sep 2010 – Apr 2017 | Provo, UT}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Completed Courses:
\begin{minipage}[t]{.25\textwidth}
\begin{tightemize}
\item Machine Design
\item Mechatronics/Robotics
\item Optimization
\end{tightemize}
\end{minipage}
%
\begin{minipage}[t]{.25\textwidth}
\begin{tightemize}
\item Thermodynamics
\item Electrical Circuits
\item Manufacturing
\end{tightemize}
\end{minipage}
%
\begin{minipage}[t]{.25\textwidth}
\begin{tightemize}
\item Numerical Methods
\item Dynamic Systems
\item Advanced Mathematics
\end{tightemize}
\end{minipage}

\vspace{1 em}

%Completed Portuguese Certification Courses including advanced grammar, literature, and Brazilian history. 

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research}
\runsubsection{BABEL}
\descript{| Undergraduate Research Assistant }
\location{May 2015 – Current | Provo, UT}
\vspace{1 em}
\begin{tightemize}
\item Perform research dedicated to exploring emerging biomedical ideas. 
\item Collaborate in a three person team developing a multi-stage expanding coronary stent and researching bioresorbable materials for degradation controllability.
\end{tightemize}

\sectionsep


\section{Experience}
\runsubsection{Missionary Training Center}
\descript{| CDL Shuttle Supervisor }
\location{Oct 2013 – May 2015 | Provo, UT}
\begin{tightemize}
\item Supervised and coordinated transportation of +200 missionaries beginning at 2 AM each day.
\item Trained 4 coworkers on driving performance and safety with CDL.
\item Inspect vehicles for safety and quality.
\item Perform consistently during all times of day and night in spite of short-notice schedule changes.
\end{tightemize}
\sectionsep
\runsubsection{North Dakota State University}
\descript{| Agricultural Research Assistant}
\location{May 2008 - Aug 2011 | Fargo, ND}
\begin{tightemize}
\item Kept extensive records and organized equipment and supply storage.
\item Oversaw the planting, thinning, weeding, and harvesting of 1600 garden plots.
\item Supervised the collection and preparation of yield samples.
\item Analyzed and documented the oil content of samples.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		SERVICE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Service}
\runsubsection{The Church of Jesus Christ of Latter-day Saints}
\descript{| Full-time Proselytizing Missionary}
\location{Sep 2011 - Sep 2013 | Brazil}
\vspace{1 em}
\begin{tightemize}
\item Worked with leadership of local congregations to coordinate teaching and fellow-shipping of prospective members.
\item Served as an office and administrative assistant coordinating calendars and clerical work. 
\item Developed advanced language skills in both spoken and written Portuguese. 
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		TECHNICAL SKILLs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\section{Technical \& Personal Skills}

\begin{minipage}[t]{.475\textwidth}
\runsubsection{Programming}

\location{ C++, Python, MatLab, and VBA Excel}  
\sectionsep
\runsubsection {ENGINEERING CAD}

\location{3D $\&$ 2D CAD in SolidWorks and NX\\
ANSYS APDL, FeBio, EAGLE}
\sectionsep
\runsubsection{RESEARCH TOOLS} 

\location {\LaTeX$~$ and MS Suite}

\end{minipage}
\hfill
\begin{minipage}[t]{.475\textwidth}

\runsubsection{MANUFACTURING SKILLS}

\location{3D Printing, machining, laser cutting and Welding} 
\sectionsep
\runsubsection{Recognitions}\\
\location{Presented at Biomedical Engineering Conference \\
Siemen Certified in NX CAD}

\sectionsep

\subsection{Languages}
\location{Portuguese Language Fluency Certificate\\
Proficient in Spanish}

\end{minipage}

\end{document}  \documentclass[]{article}