% Matthew.tex

\section{Matthew}

%%%%%%%%%% CH 7 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{entry}
\heading{Faith is More than Calling on God at the Last Day}
\source{Matthew 7:21-23}
\date{April 25, 2016}
\background{Jesus' Sermon on the Mount}
\BrText{It is a weak argument to say that we spent our life on the Lord's errand when we do not seek the truth first.  There is only one God and one true church.}{21 Not every one that saith unto me, Lord, Lord, shall enter into the kingdom of heaven; but he that doeth the will of my Father which is in heaven.
~\\
 22 Many will say to me in that day, Lord, Lord, have we not prophesied in thy name? and in thy name have cast out devils? and in thy name done many wonderful works?
~\\
 23 And then will I profess unto them, \textbf{I never knew you:} depart from me, ye that work iniquity.
 }

 \thought{
 God is Just and Merciful but doesn't yield to sin.  God has given us ample time to repent of our wrong doings.  If our heart is pure, we will be given discernment as to which church is His.  The easier path is a deadend.
 
 We work iniquity when we use the Lord's name in vain and profess to act in His behalf.  In otherwords, we need to righteously hold the priesthood and use it to serve others.  Otherwise, our example can be like that of false prophets.  Let our conduct separates us from the world.
 }
 \keyword{Church, True}
 \keyword{Work}
 \keyword{Vain}
 \keyword{Last Day}
 \keyword{False Prophets}
 \keyword{Priesthood}
 \keyword{Death Bed}
\end{entry}
